The Chemistry Development Kit (CDK): atom typing, rendering, molecular formulas, and substructure searching

### 2016-09-18 article.tex
Removed unfinished and wrong info (closes #29) and commented out an empty section

The API has hardly changed, but the internals have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better, using a honeycomb layout approach~\cite{FIXME}, % FIXME
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~\ref{fig:sdgstereo}.

@@

\subsubsection*{Hash Codes}

>>>>

The API has hardly changed, but the internals have significantly. Besides
the aforementioned overlap resolution, the engine also handles large ring
systems much better,
and handles stereochemistry of the input. Previously, double bond stereochemistry
was supported, but the new engine more efficiently uses this when creating 2D
layouts. Furthermore, the engine assigns wedge bond information based on
tetrahedral stereochemistry. These features are exemplified by the following
code and the resulting layout depiction in Figure~\ref{fig:sdgstereo}.

@@

%% \subsubsection*{Hash Codes}
